---
title: "p8105_hw5_jc5924"
output: github_document
name: Sophie Chen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```
## Problem 2
### Describe the data
```{r}
homicides=read_csv("./data/homicide-data.csv")
```
* In this homicides datafrmame, we have `r nrow(homicides)` of observations and `r ncol(homicides)` of variable that are `r names(homicides)`.

### Create a city_state variable and summarize the unsolved cases
```{r}
homicides_summary=homicides %>% 
  janitor::clean_names() %>% 
  mutate(city_state=str_c(city,state,sep = ", "),
         status=case_when(disposition=="Closed by arrest"~"solved",
                          disposition=="Closed without arrest"~"unsolved",
                          disposition=="Open/No arrest"~"unsolved")) %>% 
  group_by(city_state) %>% 
  summarize(homicides_number=n(),
            unsolved=sum(status=="unsolved"))
homicides_summary
```
### Proportion of unsolved homicides
```{r}
baltimore=prop.test(homicides_summary %>% filter(city_state=="Baltimore, MD") %>% 
                      pull(unsolved),
                    homicides_summary %>% filter(city_state=="Baltimore, MD") %>% 
                      pull(homicides_number)) %>% 
  broom::tidy() %>% 
  saveRDS(., "./data/baltimore_prop_test.rds")
```
### Prop.test for each of the cities 
```{r}
cities=homicides_summary %>% 
  mutate(prop_test=map2(.x=unsolved, .y=homicides_number, ~prop.test(x = .x, n = .y)),
         tidy=map(.x = prop_test, ~ broom::tidy(.x))) %>% 
  select(city_state,homicides_number,unsolved,tidy) %>% 
  unnest(tidy) %>% 
  select(city_state, estimate, conf.low, conf.high)
cities
```
### Plot shows estimates and CIs
```{r}
cities %>% 
  mutate(city_state=fct_reorder(city_state,estimate)) %>% 
  ggplot(aes(x=city_state,y=estimate))+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low,ymax = conf.high))+
  labs(x = "City, State",
       y = "Estimate",
       title = "Estimate Proportions and CIs for Unsolved Homicides Among Each of the Cities")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
## Problem 3
### Setup simulation with n=30, σ=5, t-test
```{r}
sim=function(n=30,mu=0,sigma=5){
     x=rnorm(n, mean=mu,sd = sigma)
     t_statistic=t.test(x,mu=0,conf.int = 0.95) %>% 
       broom::tidy()
     t_statistic
}
dataframe=vector("list", 5000)
for (i in 1:5000) {
  dataframe[[i]] = sim()
}
dataframe %>% 
  bind_rows()
```
### Repeat it for true mean
```{r}
sim_mean =
  tibble(true_mean = c(0:6)) %>% 
  mutate(
    output = map(.x = true_mean, ~rerun(5000, sim(mu = .x))),
    test= map(output, bind_rows)
    ) %>% 
  select(-output) %>% 
  unnest()
sim_mean
```
### Plot of the power and the true mean
```{r}
sim_mean %>% 
  group_by(true_mean) %>% 
  summarize(total = n(),
            rejected = sum(p.value < 0.05)) %>% 
  mutate(power=rejected/total) %>% 
  ggplot(aes(x =true_mean,y=power,color=true_mean)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    x = "True Mean ",
    y = "Power of the test",
    title = "Plot for Power of the Test over Means"
    )
```
* According to the plot above, as true mean increases, the power of the test( proportion that null which was rejected) also increases. In another words, as the size increases, power of the test increases.

### Plot showing the average estimate and the true mean
```{r}
rejected_mean = 
  sim_mean %>% 
  filter(p.value < 0.05) %>% 
  group_by(true_mean) %>% 
  summarize(ave_mean = mean(estimate))
rejected_mean
```

```{r}
sim_mean %>% 
  group_by(true_mean) %>% 
  summarize(ave_mean = mean(estimate)) %>% 
  ggplot(aes(x = true_mean, y = ave_mean)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  geom_point(data = rejected_mean,
            color = "red") + 
  geom_smooth(data = rejected_mean, se = FALSE) +
  labs(
    x = "True Mean",
    y = "Average Estimate of Mean",
    title = " Average Estimate of All Sample"
    )
```
* First, the average estimate of mean is approximately equal to the true mean for all samples. And the average estimate of mean is approximately equal to true mean only when true mean is larger. This also proves that the when size is large, the mean is a good estimator and while it is not a good approximation when effect size is small.









